### 2020-06-19 2020/wada/adaptive_domain_adaptation.tex
rewriting

The problem of catastrophic forgetting happens when the value of $a_k(h)$ has large magnitude for value of h which is output of an out-of-domain example $(x^{adv}, y^{adv})$ (adv means adversarial). Indeed, finetuning such adapter with only in-domain data, $a_k$ never encounters adversarial examples, thus does not guarantee the risk of prediction on out-of-domain examples. However, if we control the weight of $a_k(h)$ is the combination, we might reduce the wrong belief of $a_k$ on adversarial examples. We then investigate a form more flexible of the latter combination.

>>>>

The bad performance of fine-tuned model happens as the value of $a_k(h)$ of the out-of-domain example $(x^{adv}, y^{adv})$ is adversarial to the model. Indeed, by fine-tuning such adapter with only in-domain data, $a_k$ never encounters adversarial examples, thus does not guarantee the risk of prediction on out-of-domain examples. However, if we control the weight of $a_k(h)$ is the combination, we might reduce the wrong belief of $a_k$ on adversarial examples. To execute the idea, we  investigate the version of convex combination.
